---
title: "ICCSS_dota"
author: "Suschevskiy Vsevolod"
date: "04 02 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(igraph)
library(ggraph)
library(dplyr)
library(ggforce)
library(gganimate)
library(statnet)
library(intergraph)
library(network)
library(ergm)
```


reading csv with the following structure 
```{r}
#                  New_Team value        Country colour_country
# 1             CDEC Gaming     7          China        #a6d854
# 2            CDEC Avenger     1          China        #a6d854
# 3              CDEC Youth     3          China        #a6d854
```


```{r}
player_transfers_SUPREME <- read_csv("dota22/player_transfers_SUPREME.csv")
country <- read.csv("~/dotasience/countries_normal.csv", sep=";")
```

the same for the meta data

```{r}
#                  New_Team value        Country colour_country
# 1             CDEC Gaming     7          China        #a6d854
# 2            CDEC Avenger     1          China        #a6d854
# 3              CDEC Youth     3          China        #a6d854
```

filtering NA, and inner join

```{r}
#transfers_SUPREME_small <- player_transfers_SUPREME %>% dplyr::filter(dota_pl_team %in% country$New_Team)

#transfers_SUPREME_small

teams_supreme <- read_delim("~/dotasience/dota22/teams_supreme.csv", ";", escape_double = FALSE, trim_ws = TRUE)
teams_supreme <- teams_supreme %>% filter( !is.na(team_name) )
transfers_SUPREME_small <- player_transfers_SUPREME %>% dplyr::filter(dota_pl_team %in% teams_supreme$team_name)

#table(teams_supreme$country)

```


select dates

```{r}
library(stringr)
transfers_SUPREME_small$dota_pl_data <- str_replace_all(transfers_SUPREME_small$dota_pl_data, "Present", "2018-12-30")
transfers_SUPREME_small$dota_pl_data <- str_replace_all(transfers_SUPREME_small$dota_pl_data, "[?][?]", "01")
transfers_SUPREME_small <- transfers_SUPREME_small %>% dplyr::filter(!str_detect(dota_pl_data, "[0][1][0][1]") )
transfers_SUPREME_small$dota_pl_data <- str_replace_all(transfers_SUPREME_small$dota_pl_data, "[?]", "1")

transfers_SUPREME_small <-  tidyr::separate(transfers_SUPREME_small, col = dota_pl_data, into = c("come", "left"), sep=" — ")


```

#transfers

for each player I read data as __date of entering the team and date of leaving this team, and team name__ and write it as privious team, current team, date of the event and palyer`s name

```{r}
transfers_SUPREME_small <- transfers_SUPREME_small %>%  group_by(players.Player_name.i.) %>%  mutate(Old_Team = dplyr::lag(dota_pl_team, order_by = players.Player_name.i.), New_team = dota_pl_team, when = dplyr::lag(left, order_by = players.Player_name.i.), player = players.Player_name.i.) %>% na.omit() %>% select(New_team, Old_Team, when, player) %>% filter(Old_Team != New_team) %>% ungroup() %>% select(-players.Player_name.i.)

transfers_SUPREME_small <- transfers_SUPREME_small %>% arrange(when)
library(lubridate)
transfers_SUPREME_small$when = ymd(transfers_SUPREME_small$when)
#transfers_SUPREME_small <- transfers_SUPREME_small %>% dplyr::filter(!is.na(when)) %>% filter(when > "2014-08-12" )

transfers_SUPREME_small <- transfers_SUPREME_small %>% dplyr::filter(!is.na(when)) %>% filter(when > "2017-08-12" & when < "2018-06-12" )
```


```{r}
head(transfers_SUPREME_small)

#   New_team        Old_Team             when       player              
#   <chr>           <chr>                <date>     <chr>               
# 1 Mad Kings       Luccini              2018-01-01 Greedy              
# 2 MidOrFeed       Team Secret          2017-08-14 KheZu 
```


## Network

Create a network where node is a team, and link is a player

```{r}
library(igraph)
g = graph_from_data_frame(transfers_SUPREME_small)


degree <- igraph::degree(g, mode= "all")
degree <- data.frame(keyName=names(degree), value=degree, row.names=NULL)
degree <- plyr::rename (degree,c("keyName" = "New_team"))
team_colour <- left_join(degree, teams_supreme, by = c ("New_team" = "team_name"))

V(g)$country=(team_colour$country)

 = 50
before = '#009FFF'
after = '#ec2F4B'
palette2 = colorRampPalette(c(before, after))
#2560
date_colour = palette2(fine)[as.numeric(cut(as.integer(c(1:255)),breaks = fine))]

library(ggraph)
ar = arrow(angle = 30, length = unit(2, "mm"), ends = "last", type = "open")

V(g)$size = (log(igraph::betweenness(g)+0.1)+1)

g

g_layout = layout.fruchterman.reingold(g)
mylay <- layout.auto(g)
g_layout = as.data.frame(g_layout)
names(g_layout) = c("x", "y")

manual_layout <- create_layout(graph = g,
              layout = "manual", node.positions = g_layout)
```



```{r}
library("visNetwork") 

team_colour$colour <- ifelse(team_colour$country == "China", "#ffffb3", 
                       ifelse(team_colour$country == "North America", "#fb8072",
                       ifelse(team_colour$country == "South America", "#8dd3c7", 
                       ifelse(team_colour$country == "Erope", "#80b1d3", 
                       ifelse(team_colour$country == "CIS", "#bebada", "#fdb462" )))))


V(g)$color=team_colour$colour

The_International_14 <-  The_International_all[c(99:116),]
The_International_17 <-  The_International_all[c(99:116),]

####ALARM

team_colour$TI = ifelse(team_colour$New_team %in% The_International_17$name, "TI", "no")
team_colour$TI <- as.factor(team_colour$TI)

team_colour$TI <- factor(team_colour$TI, levels = c("no", "TI"))
V(g)$TI = team_colour$TI


library(readr)
earnings <- read_csv("~/dotasience/dota22/earnings.csv", 
    col_types = cols(X1 = col_skip()))

team_colour <- left_join(team_colour, earnings, by = c("New_team" = "team_name"))
team_colour$money[is.na(team_colour$money)] = 0
V(g)$earnings = team_colour$money


team_colour$rank <- ifelse(team_colour$money > 1000000, "1", 
                            ifelse(team_colour$money > 0, "2", "3")) 
V(g)$rank = team_colour$rank
V(g)$ORG = team_colour$Org
V(g)$ISORG = ifelse(is.na(team_colour$Org),"noORG", "someORG")

save(g, "graph.RData")

E(g)$stage <- (1:length(date_colour))
#  num <- E(g)$date_colour)

nodesize <- as.numeric(igraph::degree(g) * 1.25)

V(g)$GL <- ifelse(V(g)$name %in% teams_gl$Player, 1, 0)

summary(as.factor(V(g)$GL))
```


```{r}
graph = ggraph(g, layout = "fr") +
  theme_graph() +
  geom_edge_density(aes(fill = date_colour), show.legend = FALSE) + 
  geom_edge_link0(alpha = 0.3,  arrow = ar,  show.legend = FALSE) +
  geom_node_point(aes(color = as.factor(country) ), size = nodesize, shape = 1, stroke = 5, show.legend = FALSE) +
  geom_node_point(aes(alpha = as.numeric(TI)-1), color = "red", size = 2, show.legend = FALSE)
 #geom_node_text(aes(label = name), size = 2, color = 'black', repel = TRUE)
 # ggtitle("Transfers network")

graph

length(nodesize)


?geom_node_point
p <- graph + transition_states(stage, transition_length = 1, state_length = 1) +
  shadow_wake(0.5, wrap = FALSE)+
  NULL

p

animate(p, start_pause = 10, end_pause = 10, height = 900, width = 1200, fps = 20, nframes = 500)
```


```{r}
g2 <- toVisNetworkData(g)

# задем цвет узлов
g2$nodes$color = team_colour$colour

# задаем размер узлов
g2$nodes$size = scales::rescale(g2$nodes$size^2, to = c(1, 50))

# подписи при наведении
g2$nodes$title = g2$nodes$label

visNetwork(nodes = g2$nodes, edges = g2$edges, height = "800px", width = "800px") %>%
  visIgraphLayout()
```


## ERGM

remove loops to fit graph into ERGM

```{r}


g2 <- igraph::simplify(g, remove.multiple = TRUE, remove.loops = TRUE,
  edge.attr.comb = igraph_opt("edge.attr.comb"))

net <- asNetwork(g2,  amap = attrmap(newdf = NULL), loops = FALSE)
net
plot (net)


V(g)$earningsC <-  (ifelse(V(g)$earnings == 0, "poor",
                           ifelse(V(g)$earnings < 500000, "mid", "rich"))
                    )


summary(V(g)$country)
summary(V(g)$earningsC)
summary(as.factor(V(g)$TI))
summary(as.factor(V(g)$ISORG))
```


on 4 cores with increased size of a sample and decreased step for each estimation I run the model

gwesp is geometrically weighted shared partner. Each new link between A and Cn, and Cn to B, adds smaller increase in the probability to the hance of link (transfer) between A and B

```{r}
control = control.ergm( parallel=4, parallel.type="PSOCK", init = NULL, MCMLE.maxit = 70, MCMC.init.maxedges = 30000, steplength = 0.25, seed = 128)
                        #, MCMC.burnin=50000, MCMC.interval=5000, MCMC.samplesize=50000)

ergm.model_4 <-  ergm(net ~ edges + mutual + match("TI", diff=T) + nodematch('country', diff=T) + gwesp(0.5, fixed = TRUE) + nodematch("ISORG", diff=T),
            control = control)

ergm.model.name = ergm.model_4

?ergm.eta
?nodematch
?control.ergm
mcmc.diagnostics(ergm.model.name)
summary(ergm.model.name)
m1.gof <-  gof(ergm.model.name)
plot(m1.gof)
```


New structure of outgoing stars

```{r}
ergm.model_14 <-  ergm(net ~ edges + mutual + nodemix("TI", base = 1) + nodematch('country', diff=T)  + gwesp(0.5, fixed=TRUE) +ostar(2) +nodematch("ORG") , control=control.ergm(parallel=4, parallel.type="PSOCK")) 

mcmc.diagnostics(ergm.model_14)
m2.gof <-  gof(ergm.model_14)
par(mfrow=c(3,2))
plot(m2.gof)
summary(ergm.model_14)
ergm.model_14
```


compare simulated and real networks

```{r}
plot(simulate(ergm.model_4
              ),
          vertex.col=c("yellow","blue","black", "green", "red", "white", "pink")[(get.vertex.attribute(net, "country"))])

plot((net),
          vertex.col=c("yellow","blue","black", "green", "red", "white", "pink")[(get.vertex.attribute(net, "country"))])

summary(ergm.model_2)

plogis(sum(coef(ergm.model_2)[c(1,6)])) 
plogis(sum(-9.035, 0.751, 2.273))
plogis(sum(-9.035, 2.273))



plogis(sum(-9.035, 0.751
           ))
plogis(sum(-9.035, 0.426, 0.751
           ))
plogis(sum(-9.035, 0.426, 0.426, 0.751
           ))


library(stargazer)

stargazer(ergm.model_4, type = 'text', style = "asr")
?stargazer

stargazer(ergm.model_4, ergm.model_china14,title="Results", align=TRUE, no.space=TRUE, single.row=TRUE,  ci=TRUE, ci.level=0.90)
```


same model, but only for china

```{r}
china = g


china <- igraph::delete.vertices(china, V(china)$country != "China")



graph = ggraph(china, layout = "fr") +
  theme_graph() +
  geom_edge_fan(alpha = 0.1,  arrow = ar,  show.legend = FALSE) +
  geom_node_point(aes(color = as.factor(country), size = size), shape = 1, show.legend = TRUE) +
  geom_node_point(aes(alpha = as.numeric(TI)-1), color = "red", size = 2, show.legend = FALSE)
 # geom_node_text(aes(label = name), size = 1, color = 'black', repel = TRUE) +
 # ggtitle("Transfers network")

graph

china <- igraph::simplify(china, remove.multiple = TRUE, remove.loops = TRUE,
  edge.attr.comb = igraph_opt("edge.attr.comb"))

china <- asNetwork(china,  amap = attrmap(newdf = NULL), loops = FALSE)
china
plot (china)

library(snowfall)
library(Rmpi)

ergm.model_china14 <-  ergm(china ~ edges + mutual + nodemix("TI", base = 1)  + nodemix("ISORG", base=1) + gwesp(0.5, fixed=TRUE), control=control.ergm(parallel=4, parallel.type="PSOCK"))    
         
mcmc
mcmc.diagnostics(ergm.model_china14)       
summary(ergm.model_china14)
mchina.gof <-  gof(ergm.model_china14)
plot(mchina.gof)

plot(simulate(ergm.model_china14))
plot(china)
```



```{r}
europe = g
europe <- igraph::delete.vertices(europe, V(europe)$country != "Europe")



graph = ggraph(europe, layout = "fr") +
  theme_graph() +
  geom_edge_fan(alpha = 0.1,  arrow = ar,  show.legend = FALSE) +
  geom_node_point(aes(color = as.factor(country), size = size), shape = 1, show.legend = TRUE) +
  geom_node_point(aes(alpha = as.numeric(TI)-1), color = "red", size = 2, show.legend = FALSE)
 # geom_node_text(aes(label = name), size = 1, color = 'black', repel = TRUE) +
 # ggtitle("Transfers network")

graph

europe <- igraph::simplify(europe, remove.multiple = TRUE, remove.loops = TRUE,
  edge.attr.comb = igraph_opt("edge.attr.comb"))

europe <- asNetwork(europe,  amap = attrmap(newdf = NULL), loops = FALSE)
europe
plot (europe)

ergm.model_europe2 <- ergm(europe ~ edges + mutual + nodemix("TI", base = 1)  + nodemix("ISORG", base=1) + gwesp(0.5, fixed=TRUE), control=control.ergm(parallel=4, parallel.type="PSOCK")) 

summary(ergm.model_europe2)
meurope.gof <-  gof(ergm.model_europe2)
plot(meurope.gof)

plot(europe)
plot(simulate(ergm.model_europe2))
```


```{r}
CIS = g


CIS <- igraph::delete.vertices(CIS, V(CIS)$country != "CIS")


library(ggraph)
graph = ggraph(CIS, layout = "fr") +
  theme_graph() +
  geom_edge_fan(alpha = 0.1,  arrow = ar,  show.legend = FALSE) +
  geom_node_point(aes(color = as.factor(country), size = size), shape = 1, show.legend = TRUE) +
  geom_node_point(aes(alpha = as.numeric(TI)-1), color = "red", size = 2, show.legend = FALSE)
 # geom_node_text(aes(label = name), size = 1, color = 'black', repel = TRUE) +
 # ggtitle("Transfers network")

graph

CIS <- igraph::simplify(CIS, remove.multiple = TRUE, remove.loops = TRUE,
  edge.attr.comb = igraph_opt("edge.attr.comb"))

CIS <- asNetwork(CIS,  amap = attrmap(newdf = NULL), loops = FALSE)
CIS
plot (CIS)

system.time(ergm.model_CIS2 <- ergm(CIS ~ edges + mutual + nodemix("TI", base = 1)  + nodemix("ISORG", base=1) + gwesp(0.5, fixed=TRUE), control=control.ergm(parallel=4, parallel.type="PSOCK")) 
)

summary(ergm.model_CIS2)
mCIS.gof <-  gof(ergm.model_CIS2)
plot(mCIS.gof)

plot(CIS)
plot(simulate(ergm.model_CIS2))


The_International_14 %>% group_by(name) %>% summarise(n=n())
```


```{r}
Asia = g


Asia <- igraph::delete.vertices(Asia, V(Asia)$country != "Southeast Asia")


library(ggraph)
graph = ggraph(Asia, layout = "fr") +
  theme_graph() +
  geom_edge_fan(alpha = 0.1,  arrow = ar,  show.legend = FALSE) +
  geom_node_point(aes(color = as.factor(country), size = size), shape = 1, show.legend = TRUE) +
  geom_node_point(aes(alpha = as.numeric(TI)-1), color = "red", size = 2, show.legend = FALSE)
 # geom_node_text(aes(label = name), size = 1, color = 'black', repel = TRUE) +
 # ggtitle("Transfers network")

graph

Asia <- igraph::simplify(Asia, remove.multiple = TRUE, remove.loops = TRUE,
  edge.attr.comb = igraph_opt("edge.attr.comb"))

Asia <- asNetwork(Asia,  amap = attrmap(newdf = NULL), loops = FALSE)
Asia
plot (Asia)

ergm.model_Asia2 <- ergm(Asia ~ edges + mutual + nodemix("TI", base = 1)  + nodemix("ISORG", base=1) + gwesp(0.5, fixed=TRUE), control=control.ergm(parallel=4, parallel.type="PSOCK")) 

summary(ergm.model_Asia2)
mAsia.gof <-  gof(ergm.model_Asia2)
plot(mAsia.gof)

plot(Asia)
plot(simulate(ergm.model_Asia2))
```

```{r}
b1 = team_colour %>% filter(!is.na(Org)) %>% group_by(country) %>% summarise(number = n())
b2 = team_colour %>% filter(is.na(Org)) %>% group_by(country) %>% summarise(number = n())

library(dplyr)
team_colour %>% filter(!is.na(TI)) %>% group_by(country) %>% filter(TI == "TI") %>% summarise(number = n()) 

b1
b2

b1$number / (b1$number + b2$number)

remove(b1, b2)
```



```{r}
df = transfers_SUPREME_small %>% filter(New_team %in% (team_colour %>% filter(country == "Europe" & TI == "TI") %>% select(New_team) %>% pull()) | Old_Team %in% (team_colour %>% filter(country == "Europe" & TI == "TI") %>% select(New_team) %>% pull())) 

df <- unname(df)
df[,2]

df1 = data.frame(e =  rbind(df[,1], df[,2],make.row.names=FALSE), ne = rbind(df[,2], df[,1],make.row.names=FALSE) )
?rbind


df1 = df %>%  filter(df$New_team %in% (team_colour %>% filter(country == "Europe" & TI == "TI") %>% select(New_team) %>% pull()) )
df2 = df %>%  filter(df$Old_Team %in% (team_colour %>% filter(country == "Europe" & TI == "TI") %>% select(New_team) %>% pull()) )
df2 = df2[,c(2,1, 3,4)]

colnames(df1)
colnames(df2) <- colnames(df1)

df = rbind(df1,df2)

df = left_join(df, team_colour, by = c("Old_Team"= "New_team"))

df_ngr$word3 = ifelse(df_ngr$word1 %in% team_mentions$to_detect, df_ngr$word1, df_ngr$word2)
df_ngr$word4 = ifelse(df_ngr$word1 == df_ngr$word3, df_ngr$word2, df_ngr$word1)


as.vector()
```



```{r}
bn_transfers <- transfers_SUPREME_small

bn_transfers <- dplyr::left_join(bn_transfers, country_colour, by = c("New_team" = "label"))
bn_transfers <- bn_transfers[,-6]

bn_transfers <- dplyr::left_join(bn_transfers, country_colour, by = c("Old_Team" = "label"))
bn_transfers <- bn_transfers[,-7]


bn_transfers <- bn_transfers %>% 
  dplyr::rename(
    New_country = country.x,
    Old_country = country.y
    )

bn_transfers$TI_Old <- ifelse(bn_transfers$Old_Team %in% The_International_14$name, "TI", "no")
bn_transfers$TI_New <- ifelse(bn_transfers$New_team %in% The_International_14$name, "TI", "no")

bn_transfers$Org_Old <- ifelse(bn_transfers$Old_Team %in% team_colour$New_team, team_colour$Org, "no")
bn_transfers$Org_New <- ifelse(bn_transfers$New_team %in% team_colour$New_team, team_colour$Org, "no")

bn_transfers$Money_Old <- ifelse(bn_transfers$Old_Team %in% team_colour$New_team, team_colour$money, "no")
bn_transfers$Money_New <- ifelse(bn_transfers$New_team %in% team_colour$New_team, team_colour$money, "no")

write.csv(bn_transfers, file = "bn_transfers.csv")
```


## Glicko

### END OF THE SCRIPT
### END OF THE SCRIPT
### END OF THE SCRIPT
### END OF THE SCRIPT

```{r}
one <- as.data.frame(transfers_SUPREME_small$New_team)
colnames(one) <- "team"
two <- as.data.frame(transfers_SUPREME_small$Old_Team)
colnames(two) <- "team"
teams_2017 <- unique(rbind(one, two))
teams_2017$team <- as.character(teams_2017$team)
remove(one, two)
```

```{r}
transfers_SUPREME_smaller <- transfers_SUPREME_small %>% filter(New_team %in% teams_gl_2017$lp & Old_Team %in% teams_gl_2017$lp)
transfers_SUPREME_smaller$stage = ifelse(transfers_SUPREME_smaller$when <= "2017-10-01", 1, ifelse(transfers_SUPREME_smaller$when <= "2018-01-30", 2, 3))


library(igraph)
g = graph_from_data_frame(transfers_SUPREME_smaller)


degree <- igraph::degree(g, mode= "all")
degree <- data.frame(keyName=names(degree), value=degree, row.names=NULL)
degree <- plyr::rename (degree,c("keyName" = "New_team"))
team_colour <- left_join(degree, teams_supreme, by = c ("New_team" = "team_name"))

team_colour <- left_join(team_colour, teams_gl_2017, by = c ("New_team" = "lp"))

V(g)$country=(team_colour$country)

fine = 50
before = '#009FFF'
after = '#ec2F4B'
palette2 = colorRampPalette(c(before, after))
#2560
date_colour = palette2(fine)[as.numeric(cut(as.integer(c(1:216)),breaks = fine))]

library(ggraph)
ar = arrow(angle = 30, length = unit(2, "mm"), ends = "last", type = "open")

V(g)$size = (log(betweenness(g)+0.1)+1)

g_layout = layout.fruchterman.reingold(g)
mylay <- layout.auto(g)
g_layout = as.data.frame(g_layout)
names(g_layout) = c("x", "y")

manual_layout <- create_layout(graph = g,
              layout = "manual", node.positions = g_layout)



The_International_17 <-  The_International_all[c(99:116),]

####ALARM

team_colour$TI = ifelse(team_colour$New_team %in% The_International_17$name, "TI", "no")
team_colour$TI <- as.factor(team_colour$TI)

team_colour$TI <- factor(team_colour$TI, levels = c("no", "TI"))
V(g)$TI = team_colour$TI


library(readr)
earnings <- read_csv("~/dotasience/dota22/earnings.csv", 
    col_types = cols(X1 = col_skip()))

team_colour <- left_join(team_colour, earnings, by = c("New_team" = "team_name"))
team_colour$money[is.na(team_colour$money)] = 0
V(g)$earnings = team_colour$money


team_colour$rank <- ifelse(team_colour$money > 1000000, "1", 
                            ifelse(team_colour$money > 0, "2", "3")) 
V(g)$rank = team_colour$rank
V(g)$ORG = team_colour$Org
V(g)$ISORG = ifelse(is.na(team_colour$Org),"noORG", "someORG")

save(g, "graph.RData")

E(g)$stage <- (1:length(date_colour))
  num <- E(g)$date_colour

V(g)$size <- degree(g)

V(g)$GL <- team_colour$Rating
V(g)$GL2 <- team_colour$Rating2
V(g)$GL1 <- team_colour$Rating1


V(g)$name

E(g)$wave = transfers_SUPREME_smaller$stage
```

## ERGM small

```{r}
library(statnet)
library(intergraph)
library(network)
library(ergm)
library(igraph)

g2 <- igraph::simplify(g, remove.multiple = TRUE, remove.loops = TRUE,
  edge.attr.comb = igraph_opt("edge.attr.comb"))

net <- asNetwork(g2,  amap = attrmap(newdf = NULL), loops = FALSE)
net
plot (net)

V(g)$GL4 <-  (cut(V(g)$GL, breaks = 3))

V(g)$GLL <- log(V(g)$GL3)

V(g)$earningsC <-  (ifelse(V(g)$earnings == 0, "poor",
                           ifelse(V(g)$earnings < 500000, "mid", "rich"))
                    )


summary(V(g)$country)
summary(V(g)$earningsC)
summary(as.factor(V(g)$TI))
summary(as.factor(V(g)$ISORG))
```

```{r}
control = control.ergm( parallel=4, parallel.type="PSOCK", init = NULL, MCMLE.maxit = 70, MCMC.init.maxedges = 30000, steplength = 0.15, seed = 130)
                        #, MCMC.burnin=50000, MCMC.interval=5000, MCMC.samplesize=50000)

ergm.model_small <-  ergm(net ~ edges + mutual + nodematch("TI", diff=T) + nodematch('country', diff=T) + gwesp(0.5, fixed = TRUE) + nodematch("ISORG", diff=T) + absdiff("GLL") + nodematch("earningsC", diff = T),
            control = control)
#options(scipen=999)
ergm.model.name = ergm.model_small

# ?nodematch
# ?control.ergm
mcmc.diagnostics(ergm.model.name)
summary(ergm.model.name)
m1.gof <-  gof(ergm.model.name)
plot(m1.gof)
summary(ergm.model.name)
```

#Not a network
```{r}


ergm.model_4 <-  ergm(net ~ edges + match("TI", diff=T) + nodematch('country', diff=T) + nodematch("ISORG", diff=T)  + nodemix("GL4"),
            control = control)

ergm.model.name = ergm.model_4

net
mcmc.diagnostics(ergm.model.name)
summary(ergm.model.name)
m1.gof <-  gof(ergm.model.name)
plot(m1.gof)
```



#HZ cho vectory

```{r}
transfers_SUPREME_smaller


```
